# Vignette for running analysis using the RSV model and plotting figures and generating plots 

## 1. Set working directory to folder with cloned repository on your device 

## 2. Generate initial states

```{r}

# load data from Hodgson et al 2020
load(here::here("data/uk_data_sum.RData"))
load(here::here("data/posteriors.Rda"))

# load necessary functions 
source("functions/RunInterventions.R")
```

Follow instructions in `generate_initial_states.R` in /src folder to complete this step

## 3. Load model and parameters

```{r}
# load model 
source("functions/run_model_merged.R")

```
## 4. Model logic checks

To check the model logic implementation of aging, and vaccination and epidemiological movements follow the steps in `aging_check.R` and `check_health_vac.R` respectively 

## 5. Run scenarios and estimate cost-effectiveness

Open `scenarios_cost_effect.R` in /src folder to run scenarios. Also use this R script to generate the plots on model stabilization, and plots of incidence per intervention scenario.

## 6. Plotting figures

To generate figure 2 and figure 3, use the `annual_incidence.R` and `figure_3.R` script respectively in /main folder. For some plots, you may get the error below, ignore it
```{r, echo=TRUE}
 plot_incidence(results_base, " Base: No intervention", "base")

#Warning: Removed 3 rows containing missing values (`geom_line()`).
#Warning: Removed 3 rows containing missing values (`geom_line()`).
#Warning: Removed 3 rows containing missing values (`geom_line()`).
#Warning: Removed 3 rows containing missing values (`geom_line()`).

 # this is not true since there are no missing values 

 sum(is.na(results_base))
# [1] 0

```
## 7. Generating tables 

Use `tables.R` to generate all tables 

Note: The generated tables can be saved by copying to the clipboard and pasting to word or zooming in Viewer in RStudio taking a screenshot of the table. 
